Dipolar interactions in dense ensembles of Nitrogen-Vacancy centers

### 2022-06-21 Talks/Journées de l'axe/presentation.tex

\begin{document}
\begin{frame}
\maketitle
\centering
Mettre logos ici
\end{frame}
%\begin{frame}{Outline}
%\tableofcontents
%\end{frame}
%\section{Physics of the NV center}
\begin{frame}{What are NV centers and why are they everywhere?}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide  NV properties}
\end{frame}

\begin{frame}{What are NV centers and why are they everywhere ?}
\begin{itemize}
\item Good optical properties : quantum yield $\approx 1$, stable in time and temperature
\medskip
\item Good spin properties : $T_1\approx\ \rm ms$ and $T_2^*\sim \mu$s at 300 K.
\medskip
\item Optical polarization (up to 90\%) and readout (fidelity up to 0.3) of the spin at room temperature
\end{itemize}
\bigskip
$\to$ One of the most versatile spin qubit at room temperature
\end{frame}

\begin{frame}{What are NV centers being used for ?}
$\bullet$ Quantum memories :
\begin{center}
\includegraphics[width=0.8\textwidth,height=0.9\textheight,keepaspectratio]{mémoire}
\end{center}

@@

@@

\begin{frame}{Context of my PhD work : new physics with dense ensemble of NV centers}
\begin{itemize}
\item To increase the ensemble sensitivity we need to increase the density of NV centers
\item Chemists and material scientists have made huge progress to grow NV-rich diamond with little other impurities 
\begin{center}
\includegraphics[width=0.65\textwidth,height=0.9\textheight,keepaspectratio]{diamant Alex}
\end{center}
\item When the defects density reaches a critical point, many body effects start to appear due to dipole-dipole interaction and charge transfer (3 ppm of NV = 30 kHz dipole coupling between NV neighbors)
\end{itemize}
\end{frame}
\begin{frame}{Basic example : Optically Detected Magnetic Resonance (ODMR)}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{slide ODMR}
\end{frame}

@@

\begin{frame}{Other results with dense ensemble of spins}
$\bullet$ Optical detection of dark spins :
\begin{center}
\includegraphics[width=\textwidth,height=0.3\textheight,keepaspectratio]{dark spins}
\end{center}
$\bullet$ Mechanical detection of resonant dipolar coupling :
\begin{center}
\includegraphics[width=\textwidth,height=0.3\textheight,keepaspectratio]{Cr-meca}
\end{center}
\end{frame}

@@

\bigskip
\textbf{Take home messages }
\begin{itemize}
\item NV centers are defects in diamond with an optically controllable and readable spin at room temperature
\medskip
\item Many body effects start to manifest with the new NV-rich samples being made
\end{itemize}
\end{frame}
\begin{frame}{Bonus : Magnetometry in zero magnetic field}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_magneto}
\end{frame}
\begin{frame}{Optical properties of NV$^-$ centers}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{slide_NV_optical}
\end{frame}
\begin{frame}{NV$^-$ center electronic structure}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{NV_8_niveaux_3}
\end{frame}
\begin{frame}{NV center spin sub-levels}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{slide_3_niveaux}
\end{frame}
\end{document}

>>>>

\begin{document}
\begin{frame}
\maketitle
\begin{center}
\includegraphics[width=\textwidth,height=0.3\textheight,keepaspectratio]{logos}
\end{center}
\end{frame}
%\begin{frame}{Outline}
%\tableofcontents
%\end{frame}
%\section{Physics of the NV center}
\begin{frame}{What are NV centers?}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide  NV properties}
\end{frame}

\begin{frame}{What are NV centers good at ?}
\begin{itemize}
\item Good optical properties : quantum yield $> 0.9$, photostable
%\pause
\medskip
\item Good spin properties : $T_1\approx\ \rm ms$ and $T_2^*\sim \mu$s at 300 K.
%\pause
\medskip
\item Optical polarization (up to 90\%) and readout (fidelity up to 0.3) of the spin at room temperature
\end{itemize}
%\pause
\bigskip
$\to$ One of the most versatile spin qubit at room temperature
\end{frame}

\begin{frame}{What are NV centers being used for ?}
$\bullet$ Quantum memories :
\begin{center}
\includegraphics[width=0.8\textwidth,height=0.9\textheight,keepaspectratio]{mémoire}
\end{center}
%\pause

@@

%\pause

@@

\begin{frame}{Context of my PhD work : new physics with dense ensemble of NV centers}
\begin{itemize}
\item To increase the magnetic field sensitivity we need to increase the density of NV centers
%\pause
\item Chemists and material scientists have made huge progress to grow NV-rich diamond with little other impurities 
\begin{center}
\includegraphics[width=\textwidth,height=0.2\textheight,keepaspectratio]{diamant Alex}
\end{center}
%\pause
\item When the defects density reaches a critical point, many body effects start to appear due to dipole-dipole interaction and charge transfer (3 ppm of NV = 30 kHz dipole coupling rate between NV neighbors)
\end{itemize}
\end{frame}
\begin{frame}{Basic example : Optically Detected Magnetic Resonance (ODMR)}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{slide ODMR}
\end{frame}

@@

\begin{frame}{Optical detection of dark spins}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{dark spins}
\end{frame}

\begin{frame}{Mechanical detection of dipole-dipole coupling}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Cr-meca}
\end{frame}

@@

\bigskip
\textbf{Take home messages }
\begin{itemize}
\item NV centers are defects in diamond with an optically controllable and readable spin at room temperature
\medskip
\item Many body effects start to manifest with the new NV-rich samples being made
\medskip
\item These effects can be exploited for applications : detection of dark spins, magnetometry, mechanical cooling...
\end{itemize}
\end{frame}
\begin{frame}{Bonus : Magnetometry in zero magnetic field}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_magneto}
\end{frame}
\begin{frame}{Optical properties of NV$^-$ centers}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{slide_NV_optical}
\end{frame}
\begin{frame}{NV$^-$ center electronic structure}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{NV_8_niveaux_3}
\end{frame}
\begin{frame}{NV center spin sub-levels}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{slide_3_niveaux}
\end{frame}
\end{document}
